---
title: "R Package Vignette"
author: "Aditi Gopalan"
date: "07/03/2022"
output: html_document
---

```{r set3up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Setting up a new package

```{r 1.1, eval=FALSE}
library(devtools)
library(roxygen2)

setwd("C:/Users/aditi/Desktop/angsd")
devtools::create("aditi.package")
```

```
√ Creating 'aditi.package/'
√ Setting active project to 'C:/Users/aditi/Desktop/angsd/aditi.package'
√ Creating 'R/'
√ Writing 'DESCRIPTION'
Package: aditi.package
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R (parsed):
    * First Last <first.last@example.com> [aut, cre] (YOUR-ORCID-ID)
Description: What the package does (one paragraph).
License: `use_mit_license()`, `use_gpl3_license()` or friends to
    pick a license
Encoding: UTF-8
Roxygen: list(markdown = TRUE)
RoxygenNote: 7.1.2
√ Writing 'NAMESPACE'
√ Writing 'aditi.package.Rproj'
√ Adding '^AG\\.Package\\.Rproj$' to '.Rbuildignore'
√ Adding '.Rproj.user' to '.gitignore'
√ Adding '^\\.Rproj\\.user$' to '.Rbuildignore'
√ Setting active project to '<no active project>'
```
I ran the following to build my package 

```{r 1, eval=FALSE}
# # Ctrl + Shift + F10
devtools::load_all()
devtools::document()
devtools::build_vignettes()
devtools::build()
```
## 2. Use the reading in function 

I copied the function into an R script and moved that to my R folder in the package 

## 3. Adapting the DESCRIPTION file

I modified the description file. Dependencies are added automatically 

## 4. Loading and using the function 

On the scu, I ran the following and then scped the file to my local
```
scp adg4001@aphrodite.med.cornell.edu:/home/adg4001/hw/fastqc_data.txt C:\Users\aditi\Desktop\angsd\aditi.package\data

adg4001@aphrodite.med.cornell.edu's password:
fastqc_data.txt                                                                       100%   13KB   2.5MB/s   00:00
```

```{r 4, eval=FALSE}
library(magrittr) 
library(dplyr)
library(aditi.package)

source("C:/Users/aditi/Desktop/angsd/aditi.package/R/reading_in.R")
aditi.package::reading_in_alt("C:/Users/aditi/Desktop/angsd/aditi.package/data/fastqc_data.txt")
```
```
 #Base     Mean Median Lower Quartile Upper Quartile 10th Percentile 90th Percentile
1      1 39.85109     40             40             40              40              40
2      2 39.82322     40             40             40              40              40
3      3 39.80665     40             40             40              40              40
4      4 39.79661     40             40             40              40              40
5      5 39.48241     40             40             40              40              40
6      6 39.68721     40             40             40              40              40
7      7 39.61447     40             40             40              40              40
8      8 39.53904     40             40             40              40              40
9      9 39.40539     40             40             40              40              40
10    10 39.22728     40             40             40              40              40
11    11 39.03652     40             40             40              40              40
12    12 38.83685     40             40             40              40              40
13    13 38.00679     40             40             40              40              40
14    14 37.42061     40             40             40              32              40
15    15 37.22028     40             40             40              29              40
16    16 36.47826     40             40             40              22              40
17    17 35.04345     40             40             40              13              40
18    18 35.44634     40             40             40              16              40
19    19 34.87004     40             40             40              14              40
20    20 34.15579     40             38             40              11              40
21    21 33.22713     40             31             40              10              40
22    22 32.49217     40             27             40               9              40
23    23 31.41096     40             22             40               7              40
24    24 30.57500     40             20             40               6              40
25    25 29.42926     40             16             40               5              40
26    26 28.15252     40             14             40               5              40
27    27 26.80315     35             11             40               4              40
28    28 25.57454     30             10             40               4              40
29    29 24.97025     28             10             40               4              40
```
## 5 

SED command in UNIX stands for stream editor and it can perform lots of functions on file like searching, find and replace, insertion or deletion. `sed` with the `-n` prints only replaced lines.

```
source: https://www.geeksforgeeks.org/sed-command-in-linux-unix-with-examples/
```

## 6 

This takes sample name as input and adds it to the Sample_Name column in the df 

```{r 6, eval=FALSE}
dat$Sample_Name <- s_name
```
```
#Base     Mean Median Lower Quartile Upper Quartile 10th Percentile 90th Percentile
1      1 39.85109     40             40             40              40              40
2      2 39.82322     40             40             40              40              40
3      3 39.80665     40             40             40              40              40
4      4 39.79661     40             40             40              40              40
5      5 39.48241     40             40             40              40              40
6      6 39.68721     40             40             40              40              40
7      7 39.61447     40             40             40              40              40
8      8 39.53904     40             40             40              40              40
9      9 39.40539     40             40             40              40              40
10    10 39.22728     40             40             40              40              40
11    11 39.03652     40             40             40              40              40
12    12 38.83685     40             40             40              40              40
13    13 38.00679     40             40             40              40              40
14    14 37.42061     40             40             40              32              40
15    15 37.22028     40             40             40              29              40
16    16 36.47826     40             40             40              22              40
17    17 35.04345     40             40             40              13              40
18    18 35.44634     40             40             40              16              40
19    19 34.87004     40             40             40              14              40
20    20 34.15579     40             38             40              11              40
21    21 33.22713     40             31             40              10              40
22    22 32.49217     40             27             40               9              40
23    23 31.41096     40             22             40               7              40
24    24 30.57500     40             20             40               6              40
25    25 29.42926     40             16             40               5              40
26    26 28.15252     40             14             40               5              40
27    27 26.80315     35             11             40               4              40
28    28 25.57454     30             10             40               4              40
29    29 24.97025     28             10             40               4              40
   Sample_Name
1         wt_1
2         wt_1
3         wt_1
4         wt_1
5         wt_1
6         wt_1
7         wt_1
8         wt_1
9         wt_1
10        wt_1
11        wt_1
12        wt_1
13        wt_1
14        wt_1
15        wt_1
16        wt_1
17        wt_1
18        wt_1
19        wt_1
20        wt_1
21        wt_1
22        wt_1
23        wt_1
24        wt_1
25        wt_1
26        wt_1
27        wt_1
28        wt_1
29        wt_1
```
## 7 

Okay. From the reps I used for the previous assignments (I had already run fastqc), I wrote the following loop to put all the text files in one folder. 

```{bash 7.1, eval=FALSE}
for i in ERR458493 ERR458494;
do
cp /home/adg4001/alignments_bwa_star/reps/WT_1/WT_1_${i}_fastqc/fastqc_data.txt /athena/angsd/scratch/adg4001/data_package/WT_1_${i}_data.txt
done
```

I ran this in the WT_2 folder as well: 

```{bash 7.2, eval=FALSE}
for i in ERR458878 ERR458879;
do
cp /home/adg4001/alignments_bwa_star/reps/WT_2/WT_2_${i}_fastqc/fastqc_data.txt /athena/angsd/scratch/adg4001/data_package/WT_2_${i}_data.txt
done
```

I scped the files into my data folder of the package 

```
C:\Users\aditi>scp adg4001@aphrodite.med.cornell.edu:/athena/angsd/scratch/adg4001/data_package/* C:\Users\aditi\Desktop\angsd\aditi.package\data
adg4001@aphrodite.med.cornell.edu's password:
WT_1_ERR458493_data.txt                                                               100%  134KB   2.8MB/s   00:00
WT_1_ERR458494_data.txt                                                               100%  136KB   3.7MB/s   00:00
WT_2_ERR458878_data.txt                                                               100%  135KB   3.8MB/s   00:00
WT_2_ERR458879_data.txt
```

```{r 7.3, eval=FALSE}
dir <- "C:/Users/aditi/Desktop/angsd/aditi.package/data"
pat <- "*.txt"
#get a list of all files with ndvi in the name in your directory
dir 
pat 
files <- list.files(path=dir, pattern=pat, full.names = TRUE)
files
dat_1 = list()
for(file in files){
  nam = gsub("C:/Users/aditi/Desktop/angsd/aditi.package/data/", "", file)
  nam1 = gsub("_data.txt", "", nam)
  dat_1[[file]] <- aditi.package::reading_in_alt(file, s_name = nam1)
}
dat_1[[1]] <-NULL
dat_1

```
## 8 

`source: https://www.statmethods.net/management/merging.html`

```{r 8, eval=FALSE}
combined_df <- data.frame()
for(i in 1:length(dat_1)){
  combined_df <- rbind(combined_df, dat_1[[i]])
}
save(combined_df, file="C:/Users/aditi/Desktop/angsd/aditi.package/data/combined_df.rda")
```
## 9

The data directory seemed like the right spot to keep my .rda file.

Documentation is in `R > data.R` 

## 10 

As mentioned above, I did this to build my package: 

```{r 10, eval=FALSE}
devtools::load_all()
devtools::document()
devtools::build_vignettes()
devtools::build()
```

## 11

```{r 11}
library(ggplot2)
library(gridExtra)
library(stringr)
load("C:/Users/aditi/Desktop/angsd/aditi.package/data/combined_df.rda")

wt_1 = combined_df[grep("WT_1", combined_df$Sample_Name),]
wt_2 = combined_df[grep("WT_2", combined_df$Sample_Name),]


W_1 <- ggplot(wt_1, aes(`#Base`, Mean, colour=Sample_Name)) + geom_point()  + theme(legend.position="bottom")
W_2 <- ggplot(wt_2, aes(`#Base`, Mean, colour=Sample_Name)) + geom_point() + theme(legend.position="bottom")

W_2 <- W_2 + scale_fill_manual(values = c("#00AFBB", "#E7B800"))

final = grid.arrange(W_1, W_2, ncol = 2)

final

ggsave(final, device = "png", path = "C:/Users/aditi/Desktop/angsd/aditi.package/data")
```


And FINALLY, to install the package: 

```{r 11.1, eval=FALSE}
devtools::install_github("aditigopalan/package")
```



